Analyzing X-ray images in Python with scikit-image

### 2016-08-21 skimage_tomo.tex
Labeled panels in Fig. 4 (tomo gallery)

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{jupyter_example}}
    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
             plot and text output (middle), and free-form narrative text (bottom).
             This makes it ideal to record and report code-based analyses.
             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
 \label{fig:jupyter}}
\end{figure*}

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
    \caption{\csentence{Typical image processing operations with
	\texttt{scikit-image}.} From left to right and top to bottom.
	Data are synthetic, unless stated otherwise.
	\textbf{Filtering -} Top: non-local means denoising of an image
	with a fine-grained texture, acquired by \emph{in situ}
	synchrotron microtomography during
	glass melting \citep{Gouillart2012}. Bottom: total-variation
	denoising of an image with two phases, corresponding to
	phase-separating silicate melts observed by \emph{in situ
	tomography} \citep{Bouttes2015}.
	\textbf{Feature extraction -} Top: Hubble deep field (NASA,
	public domain), blob detection using the
	Laplacian of Gaussian method. Bottom: ridge detection using the
	leading eigenvalue of the Hessian matrix.
	\textbf{Segmentation - } Top: super-pixel segmentation
	of a CT slice of the human head \citep{tomo_wikipedia}, using
	Felzenszwalb's algorithm \citep{Felzenszwalb2004}. Bottom: random
	walker segmentation (right) of noisy image (top-left corner), using
	histogram-determined markers (bottom-left corner).
	\textbf{Measures -} Top: visualization of local diameter
	(color-coded on the skeleton curve) of an
	interconnected phase (represented in violet).  Bottom: particles color-coded according
	to their extent.
\label{fig:tomo_gallery}}
\end{figure*}

@@

Tomographic images often suffer from artifacts or poor signal-to-noise
ratio. Several denoising filters are available for restoring these
images, ranging from general-purpose median and bilateral
filters to those more suited to specific applications. For example, total-variation denoising \citep{Chambolle2004,
Getreuer2012} is ideal for restoring piecewise-constant images (see
Fig.~\ref{fig:tomo_gallery}), such as images with a small number of
phases encountered in materials science \citep{Bouttes2015}. Conversely,
images with a fine-grained texture are better preserved with non-local
means denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).

\texttt{scikit-image} offers a wide variety of functions for detecting
geometrical features of interest in an image. Peaks in 2D
diffraction images can be extracted using blob detection methods
\citep{Ashiotis2015}, such as the Laplacian of Gaussian method (see
Fig.~\ref{fig:tomo_gallery}). In order to detect thin boundaries, the
ridges of an image can be identified as regions for which the leading eigenvalue
of the local Hessian matrix is high (see Fig.~\ref{fig:tomo_gallery}).

Segmentation of regions of interest can be achieved using one of various
strategies, depending on the characteristics of the image. Images with a
clear contrast between regions can be segmented automatically thanks to
several thresholding algorithms, including an adaptive local thresholding
algorithm aimed at images with contrast variations. Super-pixel
algorithms \citep{Felzenszwalb2004, Achanta2012} create an
over-segmentation of images in super-pixels, by grouping pixels that are
close together both in color- and spatial distance (see
Fig.~\ref{fig:tomo_gallery}). Region-growing algorithms, such as the
morphological watershed or the random walker \citep{Grady2006}, propagate
the labels of user-defined markers through the image (see
Fig.~\ref{fig:tomo_gallery}). The active contour algorithm
\citep{Kass1988} fits snake contours to features of the image, such as
edges or high-brightness regions.

The characteristics of labeled regions (particles, porosities, organs,
\dots) resulting from a segmentation can be measured using the
\texttt{measure} submodule. The different connected components (e.g.
bubbles or non-touching particles) of a binary image are labeled with the
\texttt{measure.label} function. Properties of labeled regions such as
size, extent, center of mass or mean intensity value are accessed with
\texttt{measure.regionprops} (see Fig.~\ref{fig:tomo_gallery}). Local
characteristics of a region can be retrieved as well:
Fig.~\ref{fig:tomo_gallery} shows how the local diameter of open
porosity is measured by combining a skeletonization of the porosity
channels, and the distance transform to the other phase measured on the
skeleton.

>>>>

\begin{figure*}
    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
             plot and text output (middle), and free-form narrative text (bottom).
             This makes it ideal to record and report code-based analyses.
             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
 \label{fig:jupyter}}
\end{figure*}

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
    \caption{\csentence{Typical image processing operations with
	\texttt{scikit-image}.}
	Data are synthetic, unless stated otherwise.
	\textbf{a) Filtering -} Top: non-local means denoising of an image
	with a fine-grained texture, acquired by \emph{in situ}
	synchrotron microtomography during
	glass melting \citep{Gouillart2012}. Bottom: total-variation
	denoising of an image with two phases, corresponding to
	phase-separating silicate melts observed by \emph{in situ
	tomography} \citep{Bouttes2015}.
	\textbf{b) Feature extraction -} Top: Hubble deep field (NASA,
	public domain), blob detection using the
	Laplacian of Gaussian method. Bottom: ridge detection using the
	leading eigenvalue of the Hessian matrix.
	\textbf{c) Segmentation - } Top: super-pixel segmentation
	of a CT slice of the human head \citep{tomo_wikipedia}, using
	Felzenszwalb's algorithm \citep{Felzenszwalb2004}. Bottom: random
	walker segmentation (right) of noisy image (top-left corner), using
	histogram-determined markers (bottom-left corner).
	\textbf{d) Measures -} Top: visualization of local diameter
	(color-coded on the skeleton curve) of an
	interconnected phase (represented in violet).  Bottom: particles color-coded according
	to their extent.
\label{fig:tomo_gallery}}
\end{figure*}

@@

Tomographic images often suffer from artifacts or poor signal-to-noise
ratio. Several denoising filters are available for restoring these
images, ranging from general-purpose median and bilateral
filters to those more suited to specific applications. For example, total-variation denoising \citep{Chambolle2004,
Getreuer2012} is ideal for restoring piecewise-constant images (see
Fig.~\ref{fig:tomo_gallery} a)), such as images with a small number of
phases encountered in materials science \citep{Bouttes2015}. Conversely,
images with a fine-grained texture are better preserved with non-local
means denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery} a)).

\texttt{scikit-image} offers a wide variety of functions for detecting
geometrical features of interest in an image. Peaks in 2D
diffraction images can be extracted using blob detection methods
\citep{Ashiotis2015}, such as the Laplacian of Gaussian method (see
Fig.~\ref{fig:tomo_gallery} b)). In order to detect thin boundaries, the
ridges of an image can be identified as regions for which the leading eigenvalue
of the local Hessian matrix is high (see Fig.~\ref{fig:tomo_gallery} b)).

Segmentation of regions of interest can be achieved using one of various
strategies, depending on the characteristics of the image. Images with a
clear contrast between regions can be segmented automatically thanks to
several thresholding algorithms, including an adaptive local thresholding
algorithm aimed at images with contrast variations. Super-pixel
algorithms \citep{Felzenszwalb2004, Achanta2012} create an
over-segmentation of images in super-pixels, by grouping pixels that are
close together both in color- and spatial distance (see
Fig.~\ref{fig:tomo_gallery} c)). Region-growing algorithms, such as the
morphological watershed or the random walker \citep{Grady2006}, propagate
the labels of user-defined markers through the image (see
Fig.~\ref{fig:tomo_gallery} c)). The active contour algorithm
\citep{Kass1988} fits snake contours to features of the image, such as
edges or high-brightness regions.

The characteristics of labeled regions (particles, porosities, organs,
\dots) resulting from a segmentation can be measured using the
\texttt{measure} submodule. The different connected components (e.g.
bubbles or non-touching particles) of a binary image are labeled with the
\texttt{measure.label} function. Properties of labeled regions such as
size, extent, center of mass or mean intensity value are accessed with
\texttt{measure.regionprops} (see Fig.~\ref{fig:tomo_gallery} d)). Local
characteristics of a region can be retrieved as well:
Fig.~\ref{fig:tomo_gallery} d) shows how the local diameter of open
porosity is measured by combining a skeletonization of the porosity
channels, and the distance transform to the other phase measured on the
skeleton.
